---
title: "Clase 5: La histora de la enseñanza de las lenguas y los modelos actuales"
subtitle: 'La enseñanza de lenguas romances como L2'
author  : "Kyle Parrish"
date    : "Goethe Uni Frankurt</br>Verano 2025</br>Last update: `r Sys.Date()`"
output:
  xaringan::moon_reader:
    css: [default, hygge, my-css.css, rutgers-fonts]
    lib_dir: libs
    nature:
      countIncrementalSlides: false
      ratio: 16:9
---

```{r, setup, include=FALSE}
library(here)
knitr::opts_chunk$set(
  comment = '', fig.width = 6, fig.height = 6, message = FALSE, warning = FALSE, echo = FALSE
)
```




.center[
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
## Humans have learned languages for as long as we have been speaking them.
]

---

# La histora de la enseñanza de las lenguas 

.pull-left[
.full-width[
.content-box-grey[
.large[
**Discusión 1 (20 minutos)**

How were your language courses?

Did you use your first language?

Did you translate?

Did you learn explicit rules?

Did you learn how to pronounce words explicitely? 

]]]]


```{r, echo = FALSE}
library(countdown)

countdown(minutes = 10, seconds = 0)
```

---

# La histora de la enseñanza de las lenguas 


<br>
<br>
<br>
.center[
### [Método 1](https://methodsoflanguageteaching.byu.edu/the-grammar-translation-method).


### [Método 2](https://methodsoflanguageteaching.byu.edu/the-audiolingual-method).


### [Método 3](https://methodsoflanguageteaching.byu.edu/communicative-language-teaching).
]

---

# La histora de la enseñanza de las lenguas 

.pull-left[
.full-width[
.content-box-grey[
.large[
**Discusión 2 (20 minutos)**

Which method would you like the best as a student? As an instructor?

]]]]


```{r, echo = FALSE}
library(countdown)

countdown(minutes = 10, seconds = 0)
```

---

# Three methods of language teaching

.center[
<br>
<br>
<br>
<br>
<br>
.large[
### Grammar Translation Method
]


.large[
### Audiolingual Method
]


.large[
### Communicative Language Teaching
]]

---
.center[
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
## [Grammar Translation Method](https://methodsoflanguageteaching.byu.edu/the-grammar-translation-method).
]

---

# Grammar Translation Method

.pull-left[
.full-width[
.content-box-grey[
.large[
A classical method of language teaching focused on translation.

Deriva del método tradicional de enseñanza del griego y el latín.

Metas: poder traducir textos, desserollo intelectual.

Emphasizes written work over production 
]]]]

--

.pull-right[
.full-width[
.content-box-grey[
.large[
Uso de L1: .green[Sí]

Traducción: .green[Sí]

Aprendizaje de reglas: .green[Sí]

Enfoque en pronunciación: .red[no]
]]]]

---

# Grammar Translation Method

.large[
## Critisisms:

> **Emphasis on reading and writing and not speaking** <br> (Richards & Rodgers, 201; Zhou & Niu, 2015)]

<br>

--

.large[
> **Students do not learn to use the language for communication** <br> (Celce-Murcia, 2014) 
]

<br>

--

.large[
> **It ignores contextualised learning** and fails to expose learners to ‘authentic varieties in a ‘functional context’, which usually results in students ‘knowing’ something about the language (competence) but not being able to ‘do’ anything with that knowledge (performance). <br> (Zhou & Niu, 2015)]

---

.center[
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
## [The Audiolingual method ](https://methodsoflanguageteaching.byu.edu/the-grammar-translation-method)
]

---

# The Audiolingual method

.pull-left[
.full-width[
.content-box-grey[
.large[
Based on behaviorist theory: language can be trained through a system of reinforcement.

Views language as a **habit** that needs to be automatized via repetitive practice (drills)
]]]]

--

.pull-right[
.full-width[
.content-box-grey[
.large[
Uso de L1: .red[No]

Traducción: .red[No]

Aprendizaje de reglas: .red[No]

Enfoque en pronunciación: .green[Sí]*
]]]]

.footnote[*Sidabutar, 2023]

---

# The Audiolingual method 

.large[
## Critisisms:

> **Language learning cannot be a habit because of Universal Grammar** (Chomsky, 1959)
]

.large[
Because language learners produce novel utterances that they never heard before (poverty of stimulus), these could not have been learned purely from habit formation.]

<br>

--

.large[
> **Lack of instruction in reading**
(Saville-Troike, 1973)
]


---

.center[
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
<br>
## [Communicative language teaching](https://methodsoflanguageteaching.byu.edu/the-grammar-translation-method).
]

---
 
# Communicative language teaching (CLT)

.pull-left[
.full-width[
.content-box-grey[
.large[
CLT is an approach to the teaching of languages that emphasizes interaction

Development of **communicative competence**

Fluency Emphasis at the Expense of Accuracy

Posits L2 learners have full access to UG - adults and children learn language in fundamentally the same way.

]]]]

--

.pull-right[
.full-width[
.content-box-grey[
.large[
Uso de L1: .red[No]

Traducción: .red[No]

Aprendizaje de reglas: .red[No]

Enfoque en pronunciación: .red[No]
]]]]


---

# Communicative language teaching (CLT)

.large[
## Critisisms:

> **Lack of empirical evidence** <br> Abdulaal, M. A. A. D. (2021), Liu (2015), McLaughlin (1987), and Lightbown and Spada (2006)
]

.large[
> **Over reliance on implicit learning; lack of grammar and vocabulary instruction**
 <br> Larsen-Freeman, 2000; Spada & Lightbown, 2008
]

.large[
> **Does not consider individual differences** <br> (Qasserras, 2023)
]

.large[
> **Fluency at the expense of accuracy** <br> (Ellis, 2003)
]

---

# Resumen 

.large[
We focused on three influential language teaching methods:

- **Grammar Translation**

- **Audio-lingual method**

- **Communicative Language Teaching**
]

--

.large[
Grammar translation is the oldest, followed by audio-lingual, while current language teaching is said to be commnucative.

]

--

.large[
No single method is agreed upon in general.
]
